Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-26 paper-ieee-trans.tex
halfway on the refs

\bibitem{h2020}
\emph{Horizon 2020} -- European Commission.
[Online] Available: \url{https://ec.europa.eu/programmes/horizon2020/}
[Accessed 4 Jun. 2018].

\bibitem{aiftimiei}
A. Aiftimiei, et al.,
Improving the quality of EMI Releases by leveraging the
EMI Testing Infrastructure.
\emph{J. Phys. Conf. Ser.},
vol. 396, 2012.

\bibitem{agile-manifesto}
K. Beck, et al., (2001),
Manifesto for Agile Software Development.
[Online] Available: \url{http://www.agilemanifesto.org/}
[Accessed 4 Jun. 2018].

\bibitem{zhu}
L. Zhu, L. Bass and G. Champlin--Scharff,
DevOps and Its Practices,
\emph{IEEE Softw.},
vol. 33, n. 3, pp. 32--34, 2016.

\bibitem{soltesz}
S. Soltesz, et. al.,
Container-based Operating System Virtualization: A Scalable, High-performance Alternative to Hypervisors,
\emph{SIGOPS Oper. Syst. Rev.},
vol. 41, n. 3, pp. 275--287, 2007.

\bibitem{radatz}
J. Radatz, A. Geraci and F. Katki,
IEEE Standard glossary of softare engineering terminology.
\emph{IEEE Std. 610.12--1990}, 1990.

\bibitem{sommerville}
I. Sommerville,
Integrated requirements engineering: A tutorial.
\emph{IEEE Softw.},
vol. 14, issue 1, pp. 16--23, 2005.

\bibitem{tashtoush}
Y. Tashtoush, et al.,
Impact of programming features on code readability.
\emph{Int. J. Softw. Eng. Appl.}, 
vol. 7, issue 6, pp. 441--458, 2013.

\bibitem{buse}
R. P. Buse and W. R. Weimer,
Learning a metric for code readability.
\emph{IEEE Trans. Softw. Eng.},
vol. 36, issue 4, pp. 546--558, 2010.

\bibitem{baggen}
R. Baggen, et al.,
Standardized code quality benchmarking for improving software maintainability.
\emph{Softw. Qual. J.},
vol. 20, issue 2, pp. 287--307, 2012.

\bibitem{fenton}
N.  Fenton,  and  S.  L.  Pfleeger.
Software  Metrics:  A  Rigorous  and  Practical Approach,
\emph{International Thomson Computer
Press}, London, UK, second edition, 1997.

\bibitem{capers}
J. T. Capers.
Applied Software Measurement
\emph{McGrawHill}, 1991.

\bibitem{goodman}
P. Goodman.
Practical Implementation of Software Metrics, 
\emph{McGraw Hill}, London, 1993.

\bibitem{mccabe}
T. J. McCabe.
A   Complexity   Measure,
\emph{IEEE   Transactions   on   Software Engineering},
Vol. 2, No. 4, pp. 308-320, 1976.

\bibitem{chidamber}
S.  R.  Chidamber  and  C.  E  Kemerer.
A  metrics  suite  for  Object--oriented  design,
\emph{IEEE Trans. Software Engineering}, 
June 1994.

\bibitem{lorenz}
M. Lorenz and J. Kidd.
Object-Oriented Software Metrics: A Practical Approach,
\emph{IEEE publications}.

\bibitem{myers}
G. J. Myers and C. Sandler and T. Badgett.
The art of software testing.
\emph{John Wiley \& Sons}, 2011.

\bibitem{athanasiou}
D. Athanasiou and A. Nugroho and J. Visser and A. Zaidman.
Test code quality and its relation to issue handling performance.
\emph{IEEE Transactions on Software Engineering}, 
vol. 40, issue 7, pp. 1100--1125, 2014.

\bibitem{horgan}
J. R. Horgan and S. London and M. R. Lyu.
Achieving software quality with testing coverage measuring.
\emph{IEEE Computer},
vol. 27, issue 9, pp. 60--69, 1994.

\bibitem{cordis:datagrid}
P. Kunszt,
European DataGrid project: status and plans,
\emph{Nucl. Instr. Meth. Phys. Res. A},
vol. 502, n. 2, pp. 376--381, 2003.

\bibitem{gagliardi}
Gagliardi F., Jones B., Reale M., Burke S.,
European DataGrid Project: Experiences of Deploying a Large Scale Testbed for E--science Applications,
in \emph{Performance Evaluation of Complex Systems: Techniques and Tools, LNCS},
vol. 2459, 2002.

\bibitem{globus}
I. Foster and C. Kesselman,
Globus: a Metacomputing Infrastructure Toolkit,
\emph{Int. J. Supercomput. Appl.},
vol. 11, no. 2, pp. 115--128, 1997.

\bibitem{datagrid}
L. Momtahan and A. Martin,
e--Science Experiences: Software Engineering Practice and the EU DataGrid,
in \emph{Ninth Asia--Pacific Software Engineering Conference},
pp. 269-275, 2002.

\bibitem{agile}
Torgeir Dingsoyr, Sridhar Nerur, VenuGopal Balijepally, Nils Brede Moe,
A decade of agile methodologies: Towards explaining agile software development,
\emph{J. Syst. Softw.},
vol. 85, Issue 6, pp. 1213--1221, June 2012.

>>>>

\bibitem{h2020}
\emph{Horizon 2020} -- European Commission.
[Online]. Available: \url{https://ec.europa.eu/programmes/horizon2020/}.
[Accessed 4 Jun. 2018].

\bibitem{aiftimiei}
C Aiftimiei, A Ceccanti, D Dongiovanni, A Di Meglio and F Giacomini,
``Improving the quality of EMI Releases by leveraging the EMI Testing Infrastructure,''
\emph{J. Phys. Conf. Ser.},
vol. 396, no. 5, 2012.

\bibitem{agile-manifesto}
K. Beck \emph{et al.},
``Manifesto for Agile Software Development,'' 2012.
[Online]. Available: \url{http://www.agilemanifesto.org/}.
[Accessed 4 Jun. 2018].

\bibitem{zhu}
L. Zhu, L. Bass and G. Champlin--Scharff,
``DevOps and Its Practices,''
\emph{IEEE Softw.},
vol. 33, n. 3, pp. 32--34, 2016.

\bibitem{soltesz}
S. Soltesz \emph{et al.},
``Container-based Operating System Virtualization: A Scalable, High-performance Alternative to Hypervisors,''
\emph{SIGOPS Oper. Syst. Rev.},
vol. 41, no. 3, pp. 275--287, Mar. 2007.

\bibitem{radatz}
``IEEE Standard Glossary of Software Engineering Terminology,''
\emph{IEEE Std. 610.12--1990}, pp.1--84, Dec. 31 1990.

\bibitem{sommerville}
I. Sommerville,
``Integrated requirements engineering: A tutorial,''
\emph{IEEE Softw.}, vol. 22, no. 1, pp. 16--23, Jan.--Feb. 2005.

\bibitem{tashtoush}
Y. Tashtoush, Z. Odat, I. Alsmadi, M. Yatim,
``Impact of programming features on code readability,''
\emph{Int. J. Softw. Eng. Appl.}, 
vol. 7, no. 6, pp. 441--458, Nov. 2013.

\bibitem{buse}
R. P. Buse and W. R. Weimer,
``Learning a metric for code readability,''
\emph{IEEE Trans. Softw. Eng.},
vol. 36, no. 4, pp. 546--558, Jul. 2010.

\bibitem{baggen}
R. Baggen, J. P. Correia, K. Schill and J. Visser,
``Standardized code quality benchmarking for improving software maintainability,''
\emph{Softw. Qual. J.},
vol. 20, no. 2, pp. 287--307, Jun. 2012.

\bibitem{fenton}
N. Fenton  and  S.  L.  Pfleeger,
``Software  Metrics:  A  Rigorous  and  Practical Approach,''
\emph{International Thomson Computer Press},
London, UK, second edition, 1997.

\bibitem{capers}
J. Capers,
``Applied Software Measurement (2nd Ed.): Assuring Productivity and Quality,''
\emph{McGraw Hill}, New York, NY, USA, 1997.

\bibitem{goodman}
P. Goodman,
``Practical Implementation of Software Metrics,''
\emph{McGraw Hill}, New York, NY, USA, 1993.

\bibitem{mccabe}
T. J. McCabe,
``A Complexity Measure,''
\emph{IEEE Trans. Softw. Eng.},
vol. 2, no. 4, pp. 308--320, Dec. 1976.

\bibitem{chidamber}
S. R. Chidamber and C. E. Kemerer,
``A metrics suite for Object--oriented design,''
\emph{IEEE Trans. Softw. Eng.},
vol. 20, no. 6, pp. 476--493, Jun 1994.

\bibitem{lorenz}
M. Lorenz and J. Kidd,
\emph{Object--Oriented Software Metrics: A Practical Approach}.
Prentice-Hall, Inc., Upper Saddle River, NJ, USA, 1994.

\bibitem{myers}
G. J. Myers, C. Sandler and T. Badgett,
\emph{The art of software testing, 3rd Ed.}.
Wiley Publishing, Dec. 2011.

\bibitem{athanasiou}
D. Athanasiou, A. Nugroho, J. Visser and A. Zaidman,
``Test Code Quality and Its Relation to Issue Handling Performance,''
\emph{IEEE Trans. Softw. Eng.},
vol. 40, no. 11, pp. 1100--1125, Nov. 2014.

\bibitem{horgan}
J. R. Horgan, S. London and M. R. Lyu,
``Achieving software quality with testing coverage measuring,''
\emph{Comput.},
vol. 27, no. 9, pp. 60--69, Sep. 1994.

\bibitem{cordis:datagrid}
P. Kunszt,
``European DataGrid project: status and plans,''
\emph{Nucl. Instr. Meth. Phys. Res. A},
vol. 502, no. 2, pp. 376--381, Apr. 2003.

\bibitem{gagliardi}
F. Gagliardi, B. Jones, M. Reale and S. Burke,
``European DataGrid Project: Experiences of Deploying a Large Scale Testbed for E--science Applications,''
in \emph{Performance Evaluation of Complex Systems: Techniques and Tools,}
Performance 2002. LNCS, vol. 2459, pp. 480--499, 2002.

\bibitem{globus}
I. Foster and C. Kesselman,
``Globus: a Metacomputing Infrastructure Toolkit,''
\emph{Int. J. High Perfor. Comput. Appl.,}
vol. 11, no. 2, pp. 115--128, Jun. 1997.

\bibitem{datagrid}
L. Momtahan and A. Martin,
``e--Science Experiences: Software Engineering Practice and the EU DataGrid,''
in \emph{Ninth Asia--Pacific Software Engineering Conference},
pp. 269--275, Dec. 2002.

\bibitem{agile}
T. Dingsoyr, S. Nerur, V. Balijepally and N. B. Moe,
``A decade of agile methodologies: Towards explaining agile software development,''
\emph{J. Syst. Softw.},
vol. 85, no. 6, pp. 1213--1221, Jun. 2012.
